---
title: "Cabbages"
author: "Adrian Cruz"
date: "September 18, 2024"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

$H_0$: There is no difference in the average ViC between c39 and c52 methods.  
$H_A$: There is a stastical difference in the average VitC between c39 and c52 methods. 

VitC~Cult; Numerical~Catagorial
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

```{r}
plot(VitC~Cult,data=veggy)
```

This graph shows that on average, the c39 method has lower VitC levels than the c52 method.

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results

```{r}
favstats(VitC~Cult,data=veggy)
```

Based on this chart, we can see that there is a difference between the methods c39 and c52 by looking at their means. While c39 is averaging a mean of 51.5, c52 has a higher average mean of 64.4, proving the c52 method to have more VitC.
<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results

```{r}
t.test(VitC~Cult,data=veggy)
```

Because this p-value = 3.405e-08, it is significally lower then 0.05 meaning we must reject the null hypothesis. This can conclude that the c52 method has higher levels of VitC then c39, showing their difference.
<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

Wanted to test if there was a difference in VitC between c52 and c39 cultivation methods. Provided evidence and stastical data to prove that there was a difference between the two, ulitimatley rejecting the null hypothesis and showing that the c52 method has a higher level of VitC than the c39 method.
<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
